\documentclass[9pt]{extarticle}
\usepackage{resume}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Credit %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[pdftex,
            pdfauthor={Tsion Behailu, Vania Speedy},
            pdftitle={Tsion Behailu - Resume},
            pdfsubject={Tsion Behailu - Resume},
            pdfkeywords={tsion, behailu, resume},
            pdfproducer={Created using LaTex},
            pdfcreator={pdflatex}]{hyperref}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sffamily            
\usepackage{hyperref}
\title{Resume Template}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\name{\textbf{Grace Eunbe Kim}}
{\url{https://www.linkedin.com/in/graceeunbekim}}
{eunbegracekim40@gmail.com, (510)-990-5090}
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-12pt}
\header{Education}
\begin{body}
	\textbf{University of California, Berkeley} 
    \hfill 
    \emph{December 2014 Graduate}\\
	\emph{Major: Computer Science}\\
	\emph{Bachelor's Degree}
\end{body}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Skills}

\begin{body}
	\begin{itemize}
    \itemsep -2pt
	\item Ruby, Python, Java, JavaScript, C/C++/C\#, Objective-C, HTML, CSS  
	\item Node.js, Ruby on Rails, ipython, Capybara, Selenium Webdriver, JSON, AWS, MySQL, AWS EC2, XML
	\end{itemize}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Experience}
\begin{body}
\vspace{1pt}

\textbf{Developer Programs Engineer} - 
\emph{Vungle, San Francisco, CA} 
\hfill 
\emph{November 2015 - Current}\\
\vspace*{-4pt}
\begin{itemize} 
\itemsep -0pt
    \item Developing a new generation of ad innovation which is to create internal software solutions and applications to assist Sales and other business partners to increase revenue.
    \item Investigate, research and understand user problems and trends.

\end{itemize}

\textbf{Software Engineer in Test} - 
\emph{Zendesk, San Francisco, CA} 
\hfill 
\emph{March 2015 - October 2015}\\
\vspace*{-4pt}
\begin{itemize} 
\itemsep -0pt
    \item  Developing automated acceptance test suites and tools to expand the Zendesk's testing framework for the web application and continuously contributing to the company's success in delivering a beautifully simple and customer-friendly CRM product.
	\item Performing creative exploratory testing of new features  and determining self-directed projects in an extremely fast-growth and scrum/agile environment. 
	\item Providing critical feedback to both software engineers and product managers to improve new features and capabilities within the product.
\end{itemize}	



\textbf{Software Development Engineering Intern} - 
\emph{Amazon, Seattle, WA} 
\hfill 
\emph{May 2014 - Aug 2014}\\
\vspace*{-4pt}
\begin{itemize} 
\itemsep -0pt
  \item Main lead for Amazon Web Services Diagnostics project, collecting fundamental data including registry keys and values, and results wmi queries from an EC2 Windows instance, effectively diagnosing the cause of an issue and improving instance setup.
  \item Served as full-stack back-end developer of creating data collection data and analysis program, improving user navigation with buttons instead of using a console.
  \item Developed master understanding and knowledge in Amazon Web Services, Multithreading, Asynchronization, Factory Pattern, and .Net library. 
\end{itemize}

\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Projects}
\begin{body}

\textbf {Callisto ReInvented} 
\hfill 
\emph{October 2014}\\
\url{https://github.com/jassicacanidy/CallistoReinvented}
\vspace*{-4pt}
\begin{itemize}
	\item Full-stack web development with Ruby on Rails framework to improve job searching experiences for UC Berkeley students. Reinventing and redesigning Callisto (a current job searching webpage for UC Berkeley students).
\end{itemize}

\textbf {Government Data Analysis Using IPython and NBViewer} 
\hfill 
\emph{October 2014}\\
\url{https://github.com/graceeunbekim/Airplane_crash_data_analysis}
\vspace*{-4pt}
\begin{itemize}
    \item Using REST API to grab government job data to analyze and answer what are the popular areas in the states where a lot of computer science jobs are open and salary range for a particular agency.
\end{itemize}
\vspace*{-1pt}


\textbf {Personal Website 2.0} 
\hfill 
\emph{October 2015}\\
\url{graceeunbekim.herokuapp.com}
\vspace*{-3pt}
\begin{itemize}
	\item A responsive node.js app for setting up a personal website putting all personal resources such as Linkedin profile, git profile, my projects, and contact information.
\end{itemize}
\end{body}


%%%%%%%%%%%%%%%%%%%%%%%%%%%% Coursework %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Coursework}

\begin{body}
\vspace{-11pt}
	
\begin{multicols}{3}
  \begin{itemize}
    \itemsep -2pt
    \item Computer Science(Efficient Algorithms and Intractable Problems) (170)
    \item Information(Database Management) (257 (Graduate Course))
    \item Information(Working with Open Data) (290T (Graduate Course))
    \item Computer Science(Software Engineering) (169)
    \item Computer Science(Artificial Intelligence) (188)
    \item Computer Science(Security) (161)
  \end{itemize}
\end{multicols}

\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Activities %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Activities}

\begin{body}

  \textbf{Web Summit 2014} 
  \emph{Women in Tech UC Berkeley representative}
  \hfill 
  \emph{October 2014}
  \begin{itemize}[label=\hfill]
  \item Was a selected scholar for women in tech program at the Web Summit 2014 to represent female engineers and connect with diverse women from all over the world to encourage our community.
  \end{itemize}

  \textbf{NYC Startup Odyssey 2014} - 
  \emph{Student Scholar} 
  \hfill 
  \emph{October 2014}\\
  \begin{itemize}[label=\hfill]
  \item was a selected scholar from the West Coast to attend one of the biggest hiring event in NYC to connect with tech industries in the East Coast.
  \end{itemize}


\end{body}

\end{document}